RNA-seq from 4 cell populations

### 2021-08-02 deconvolution/fans4/molec_profiling.Rmd
bug fix

rnaseq_sample_id = fread(file_counts, header = TRUE, skip = 2, nrows = 1)
gtex_sample = gtex_sample[gtex_sample$SAMPID %in% colnames(rnaseq_sample_id),]

@@

```{r PCA.gtex}

id = gtex_sample$SAMPID[which( gtex_sample$SMTSD == 'Brain - Frontal Cortex (BA9)')]
countsCombined = merge(geneCounts, gtex_count[,id], by="row.names")
rownames(countsCombined) = countsCombined$Row.names
countsCombined$Row.names = NULL

# isexpr = rowSums(edgeR::cpm(countsCombined)>1) >= 0.3*ncol(countsCombined)
isexpr = filterByExpr(countsCombined, model.matrix(~CellType, countsCombined))

>>>>

rnaseq_sample_id = fread(file_counts, header = TRUE, skip = 2, nrows = 1)
gtex_sample = gtex_sample[gtex_sample$SAMPID %in% colnames(rnaseq_sample_id),]
rownames(gtex_sample) = gtex_sample$SAMPID

@@

```{r PCA.gtex}
id = gtex_sample$SAMPID[which( gtex_sample$SMTSD == 'Brain - Frontal Cortex (BA9)')]
countsCombined = merge(geneCounts, gtex_count[,id], by="row.names")
rownames(countsCombined) = countsCombined$Row.names
countsCombined$Row.names = NULL

df_info = data.frame(CT = c(as.character(info$CellType), gtex_sample[id,]$SMTSD))

# isexpr = rowSums(edgeR::cpm(countsCombined)>1) >= 0.3*ncol(countsCombined)
isexpr = filterByExpr(countsCombined, model.matrix(~CT, df_info))
